%
% A starter on component testing
%
\section{Component Testing}
\label{sec:component}

Component testing is intended to verify functionality of a library or module as a whole and should return a true/false result. Specifically, these will
be developed in conjunction with the build out of each component/library as new features are completed. They should in all
cases be functional whether or not external dependencies are present (though some features they test for may only be enabled
when external dependencies are present). While not a complete or comprehensive list, the currently the existing set of component test are listed below. 
They are not yet run automatically, but will eventually be incorporated into the continuous integration (CI) test suite.

\begin{enumerate}
 \item Containers:
 \begin{enumerate}
      \item  TestArrayWrapper.cc  - Verifies the functionality of N-D array wrapper classes.
      \item  TestTableContainer.cc - Verifies the functionality of the table container class.
      \item  TestScalarContainer.cc  - Verifies the functionality of the scalar container class.
      \item TestVectorContainer.cc - Verifies the functionality of the vector container class.
\end{enumerate}
    \item Math:        
\begin{enumerate}
 \item     TestFastFourierTransform.cc - Verifies the functionality of the native 1-D FFT code, and if FFTW3 is enabled, the 1-D FFTW3 transformation code.
\end{enumerate}
\item Message
\begin{enumerate}
 \item TestMessenger.cc - Verifies the functionality of the messaging library.
\end{enumerate}
\begin{enumerate}
 \item  TestMK4Import.cc - Verifies the interface with the legacy dfio library and the functionality of data importation from Mk4 data types to new native data containers.
 \item TestMK4VexInterface.cc - Verifies the functional of the interface to the legacy vex library.
\end{enumerate}
\item Operators:
\begin{enumerate}
 \item TestMultidimensionalFastFourierTransform.cc  - Verifies the functionality of the N-D FFT code, and if FFTW3 is enable, the N-D FFTW3 transformation code.
 \item TestReducer.cc - Verifies that the array reduction operator is functional (e.g. summation along a specified dimension).
\end{enumerate}
\item Utilties:
 \begin{enumerate}
    \item TestIntervalLabelTree.cc - Verifies the functionality of the axis interval label tree.
    \item TestTimeStampConverter.cc - Verifies the functionality of the data/time stamp converter class.
    \item TestMultiTypeMap.cc - Verifies the functionality of the multi-type map class as a meta data container.
 \end{enumerate}
\end{enumerate}




in the presence of different version of dependencies.

%this can be words about component testing with scripts

%\subsection{Component testing to be applied to following requirements}
%\label{sec:componentreqs}



%
% eof
%
