%
% A starter on coverate and unit testing
%
\section{Test Oracle}
\label{sec:oracle}
HOPS 3 being the previous release will be used as a test Oracle for HOPS 4. This means that
results from HOPS 4 will be compared with the results and expected behavior of HOPS 3 using
the same test data. The interface and otherwise expected functionality of the commandline UI
and its output will be tested in the same manner. The following requirements will all be tested
in this manner.

%this can be words about the test oracle with scripts

\subsection{Regression testing to be applied to following requirements}
\label{sec:oraclereqs}

\begin{description}
%File I/O and Supported File Types
\reqid{D} HOPS4 shall incorporate a C-library to interface with the legacy
  \acs{Mk4} data types (stored \acs{bigendian}) in their current form for
  testing purposes, and in order to access archived data.

% A-tools
\reqid{A} The \acs{alist} program shall generate valid \acs{A-list} files in
  version 6.
\reqid{A} The \acs{adump} program shall provide valid ASCII text representations
  of columns of data from an \acs{A-list} of version 6.

% Post Processing and Fringe Plots
\reqid{A} HOPS4 shall maintain the \acs{fourmer} tool, which shall properly
  relabel channels when it combines two sub-bands.
\reqid{A} The \acs{fringex} program shall retain existing functionality to rotate
  fringes with respect to fourfit fringe solutions.
\reqid{A} The ``average'' capability, implemented by \acs{average} used in
  concert with \acs{fringex} to subdivide explore and average fringes, shall be
  preserved with equivalent functionality.
\reqid{A} The functionality of the program \acs{cofit} shall be preserved.
\reqid{A} The current functionality of the program \acs{search} shall be
  preserved.
\reqid{A} The ability to explore fringes (as is currently done with the
  combination of \acs{fringex}, \acs{average} and search must be preserved.
  HOPS4 shall support \acs{Python} scripting to aid the user in searching
  fringe space.
\reqid{P} It should be possible to make 2D plots of the type currently possible
  within \texttt{\acs{aedit}} of HOPS3.
\reqex{The HOPS3 version of \acs{fourfit} provides a fixed fringe summary
  plot. HOPS4 should have an interactive plotting capability to enable zooming
  and viewing fourfit results with an expanded scale.}
\reqid{D} Replace the existing \acs{fourfit} control file with a
  \acs{Python}-based control file. Currently existing functionality shall be
  preserved.
\reqex{The existing control file should continue to be supported. The new
  control file functionality will not likely be back-ported to HOPS3.}
\end{description}

%
% eof
%
