%
% section to cover legacy code
%
\section{Legagy Software}

The transition from HOPS 3 to HOPS 4 is sufficiently disruptive that proper
regression from the old tools to the new tools (with enhance functionality)
needs preservation.  As part of the migration from the SVN repository (that
supported HOPS 3 development) into the GIT repository (that supports HOPS 4
development) there is an opportunity to retain code that might prove useful
to the ngEHT effort.  As a practical necessity, the EHT must function as a
working array during the HOPS 4 development, so there may also be additional
changes to HOPS 3 (bug fixes) or critical functional patches (i.e., bandpass
correction for NOEMA).

Consequently, the GIT repository will contain copies of the HOPS 3 code to
allow regression testing.  This also mitigates against development slip in
that code that might otherwise be overhauled for future extension may continue
to function as it currently exists.  This is particularly true of A-list based
processing where major format changes are not likely (or which would be
encapsulated within the afio library).

To avoid confusion, applications that bear the same name (so that scripts may
still continue to function) shall follow the Python 2 to 3 migration approach
where a 3 or a 4 is appended to the executable name.  A user-selectable
configuration option then allows to specify which version is used for the
original name.  (I.e.,
\texttt{python} gets you 
\texttt{python2} or 
\texttt{python3}, depending on user choice.)

A second reason for this approach is that modified/developmental versions may
in some cases leverage existing code (not yet rewritten) which allows for
functional versions of many of the applications of the package prior to the
completion of the rewrite.  This allows use of HOPS 4 with EHT data prior to
completion of the project.  This is not intended for science use (use of
un-released code is not allowed) but rather as part of our effort to continue
to assess the development of HOPS 4.

Applications that we expect to survive in legacy form likely includes:
\texttt{adump},
\texttt{aedit},
\texttt{alist},
\texttt{average},
\texttt{cofit},
\texttt{fourfit},
\texttt{fourmer},
\texttt{fplot},
\texttt{fringex},
and
\texttt{search}.

%
% eof
%
